### 2022-06-08 main.tex
minor consensing

High values of $\delta$ required for the nonlinear effects of asymptomaticity on deaths may seem unrealistic---in practice, $\delta$ cannot be greater than the amount of post-symptomatic transmission.
While several studies have estimated the proportion of pre-symptomatic transmission to be around 30\%--60\% for the SARS-CoV-2 wildtype strain, many of them were likely subject to intervention and behavioral effects already as they were conducted after SARS-CoV-2 awareness became widespread \citep{he2020temporal}.
Instead, \cite{sender2021unmitigated} recently estimated that the proportion of pre-symptomatic transmission can be as low as 20\% (95\%CI: 6\%--32\%) during the first few weeks of the pandemic when the pandemic-awareness and intervention measures were minimal.
There are two implications for the discrepancy in the estimates of the proportion of presymptomatic transmission---first, a low proportion of presymptomatic transmission suggests that high $\delta$ values are feasible (although not necessarily likely) relative to the initial pandemic phase; and second, intermediate levels of behavioral effects ($\delta > 0$) would have been already present early in the pandemic to reduce the proportion of presymptomatic transmission from 20\% to 60\%.
\jd{We need to be a bit more nuanced here: we get the low value by focusing on just a couple of weeks, so we're sort of suggesting a counter-factual where nobody notices COVID for a long time.}
\swp{How's this?}

>>>>

High values of $\delta$ required for the nonlinear effects of asymptomaticity on deaths may seem unrealistic---in practice, $\delta$ cannot be greater than the amount of post-symptomatic transmission.
While several studies have estimated the proportion of pre-symptomatic transmission to be around 30\%--60\% for the SARS-CoV-2 wildtype strain, many of them were likely subject to intervention and behavioral effects already as they were conducted after SARS-CoV-2 awareness became widespread \citep{he2020temporal}.
Instead, \cite{sender2021unmitigated} recently estimated that the proportion of pre-symptomatic transmission can be as low as 20\% (95\%CI: 6\%--32\%) during the first few weeks of the pandemic when the pandemic-awareness and intervention measures were minimal.
There are two implications for the discrepancy in the estimates of the proportion of presymptomatic transmission---first, a low proportion of presymptomatic transmission suggests that high $\delta$ values are feasible (although not necessarily likely) during the initial pandemic phase; and second, intermediate levels of behavioral effects ($\delta > 0$) would have been already present early in the pandemic to reduce the proportion of presymptomatic transmission from 20\% to 60\%.
